Issues with Dynamical Measurements Across the Disk

### 2019-02-20 paper/ms.tex
Small edits, remove comments

%where is Figure 4 referred to? we should include a discussion of it before starting the next section

@@

%First, a dark matter only simulation was run with $\Lambda$CDM cosmology parameterized by $\Omega_m = 0.272$, $\Omega_{\Lambda} = 0.728$, $\Omega_b = 0.0455$, $h = 0.702$, $\sigma_8 = 0.807$, and $n_s = 0.961$, consistent with current constraints \citep{2018arXiv180706209P}. Halos are selected at $\z=0$ based solely on their mass ($\sim 1\text{--}2 \times 10^{12} \Msun$).  Particles within $5 R_{200\text{m}}$ of each halo are traced back to $\z=99$ and the initial conditions are regenerated at higher resolution using MUSIC \citep{2011MNRAS.415.2101H}.

%Simulations were run using \texttt{GIZMO}\footnote{\url{http://www.tapir.caltech.edu/~phopkins/Site/GIZMO.html}} \citep{2015MNRAS.450...53H}. Hydrodynamics is solved using the meshless finite-mass method and gravity is solved using a modified version of the Tree-PM solver of \texttt{GADGET-3}, using fully adaptive and fully conservative gravitational force softening for gas.

These simulations contain dark matter particles of mass $\sim$35,000 \Msun,
gas particles of mass $\sim 7000 \text{--} 20,000\,\Msun$, and star particles
of mass $\sim 5000 \text{--} 7000\,
\Msun$,\footnote{In fact, the simulation m12i contained a gas
splitting bug which causes a small number of gas and star particles to have
larger than typical masses. These constitute only $\sim0.2\%$ of the star
particles in the $\z=0$ snapshots, and are only a factor of a few more massive
than typical star particles. Since our results are broadly consistent between
the three simulations, we ignore this minor complication.} with the lower end
coming from stellar evolution \citep{2018arXiv180610564S}. Softening lengths
for dark matter and star particles are fixed at $112\,\pc$ and $11.2\,\pc$,
respectively.\footnote{This is $2.8$ times the often-quoted
Plummer-equivalent.} The gas softening length is adaptive, but at $z=0$ the
median softening length for gas particles around roughly solar positions (with
cylindrical radii within $500\,\pc$ of $8.2\,\kpc$ and $\abs{z}<1\,\kpc$) is
$98\,\pc$.

>>>>

@@

These simulations contain dark matter particles of mass $\sim35,000\,\Msun$,
gas particles of mass $\sim 7000 \text{--} 20,000\,\Msun$, and star particles
of mass $\sim 5000 \text{--} 7000\,
\Msun$,\footnote{In fact, the simulation m12i contained a gas
splitting bug which causes a small number of gas and star particles to have
larger than typical masses. These constitute only $\sim0.2\%$ of the star
particles in the $\z=0$ snapshots, and are only a factor of a few more massive
than typical star particles. Since our results are broadly consistent between
the three simulations, we ignore this minor complication.} with the lower end
coming from stellar evolution \citep{2018arXiv180610564S}. Softening lengths
for dark matter and star particles are fixed at $112\,\pc$ and $11.2\,\pc$,
respectively.\footnote{This is $2.8$ times the often-quoted
Plummer-equivalent.} The gas softening length is adaptive, but at $z=0$ the
median softening length for gas particles around roughly solar positions (with
cylindrical radii within $500\,\pc$ of $8.2\,\kpc$ and $\abs{z}<1\,\kpc$) is
$98\,\pc$.
